---
title: "Exercise 4 Solution"
format: docx
editor: visual
---

## Exercise 4

In RStudio, create a new Quarto doc and do the following.

1.  Load the tidyverse.
2.  Import and join `customer_data` and `store_transactions`.
3.  Explore this combined dataset using the functions we've covered.
4.  Provide at least one interesting numeric summary and one interesting visualization that include continuous variables.
5.  Practice good coding conventions as discussed.
6.  Render the Word doc and upload to Canvas.

Five points total, one point each for:

\- Loading the tidyverse.

\- Provide at least one numeric summary.

\- Provide at least one visualization.

\- Following good coding conventions (piping, comments, etc.).

\- Submitting a rendered Word doc.

```{r}

# Load the tidyverse.

library(tidyverse)
```

```{r}

# Import data.

customer_data <- read_csv("customer_data.csv")
store_transactions <- read_csv("store_transactions.csv")

crm_data <- customer_data |> 
  left_join(store_transactions, join_by(customer_id))
```

```{r}

# At least one interesting numeric summary.

crm_data |> 
  group_by(region) |> 
  summarize(
    n = n(),
    recent_transactions = sum(dec_2018)
  ) |> 
  mutate(avg_transactions = recent_transactions / n)
```

```{r}

# At least one interesting visualization.

crm_data |> 
  mutate(age = 2026 - birth_year) |> 
  ggplot(aes(x = age, y = dec_2018)) +
  geom_jitter(size = 2, alpha = 0.5) +
  facet_grid(~ region) +
  labs(
    title = "December 2018 Purchases by Age and Region",
    x = "Age",
    y = "December 2018 Purchases")

```
